# Introduction {#intro}

## Markdown syntax
Markdown is a simple text-based way of formatting documents. There are many flavors of markdown, we'll start with standard markdown and then add some specific rmarkdown information. Let's look at some other basics:

- You can put text into *italics* and **bold** using \* or \*\*
- To create headings, put one or more \# symbols at the beginning of a line, followed by a space. One \# is for a level one header, \#\# for a level two header, etc.
- To make bullet lists (such as this one), just start lines with a -; you can get additional levels by starting a line a couple of spaces or a tab in. Numbered lists work the same way using 1. 2. 3.
  
   ```
    - Topic 1
    - Topic 2  
    - Topic 3
      - Topic 3a
  ```
- To cite code (including markdown syntax as above) use \` on both sides for short bits and  \`\`\` in a separate line above and below larger codeblocks.
- Quote text using > at the beginning of the line (maybe you remember this from old e-mail programs?)

  ```
  > This is a Quote
  ```

- A link is set putting the text that you want to highlight in square brackets followed by the link in round brackets. Don't forget to include http:// or https:// at the beginning of the link

  ```
  [This is a link](http://www.example.com)
  ```
- You can find more markdown formatting options [here](https://guides.github.com/features/mastering-markdown/). Note that markdown comes in different dialects, referred to as "flavors". We are mainly going to be using elements that are part of a consensus referred to as [Common Markdown](http://commonmark.org/), though you can use any other components of the github flavored markdown linked above.

## Bookdown Specific Features

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].